```{r setup, echo = FALSE, results = "hide"}
source("~/work/ecodatascripts/vars/crowns/model/fit-models.R")
specTable <- table(dat$spec)[table(dat$spec) != 0]
elevSpecTable <- table(dat$spec, dat$elevcl)
```

## These scripts predict crown dimensions
Crown depth (distance from lowest to highest point of crown) and crown area (as a horizontal slice through the crown at its widest position) are predicted.  The predictions are constructed using data collected in 1986/87.  Data was available for the following species/elevations:
```{r table, echo = FALSE}
elevSpecTable
```
Due to limited data, models were constructed for the following species/combinations of species: ABBA, PIRU, BECO/BEAL/BEPA (combined into one model), and all hardwoods combined.  Each of the four groups was modeled at three elevations (L/M/H).

## Models



<!-- ### Method to calculate z-values -->
<!-- 1. $z = r\cos(\theta_B) \tan(\theta_S)$, where $\theta_B$ is the angle between the slope aspect and the vector from a given point through the origin, $\theta_S$ is the slope angle. and $r$ is the distance from the origin to the point. -->
<!--   * $\theta_B$ is calculated from dot product of the projection of the slope aspect onto the 2d plot, $a$, and the vector from a given point through the origin, $b$: -->
<!--   * $\theta_B = cos^{-1} ( \frac{ a \cdot b } {|a||b| } )$ -->
<!--   * Using this method, if $\theta_B > 90^{\circ}$, then $z$ will be a negative value, ie. downslope from the center of the plot. -->
<!-- 2. Notes -->
<!--   * Due to machine precision error with the arccos function, $\frac{a \cdot b}{|a||b|}$ was rounded to 15 digits (machine precision ~ $2e-16$).  When $a \cdot b$ is very close to $|a||b|$, (i.e. they are the same in reality), the fraction is sometimes computed to be slightly greater than 1 on the machine which leads to a NAN result when passed to the arccos function in R. -->

<!-- ### Moosilauke -->
<!-- * On Moosilauke, each plot has an azimuth and slope calculate along the azimuth.  Z-value are calculated from these values in addition to plant x,y coordinates. -->
<!-- * The y-axis is oriented along NW -\-> SE direction for Moosilauke plots. -->
<!-- * The slope azimuth points downslope.  So, the slope from the top of the plot looking downhill through the origin. -->

<!-- ## Example: Moosilauke permanent plot 22  -->

<!-- The aspect of this plot points directly west ($270^\circ$) -->
<!-- ### Data and function dependencies -->
<!-- ```{r data} -->
<!-- source("~/work/ecodatascripts/vars/z-values/functions.R") -->
<!-- dat <- read.csv("~/work/data/moose/moose-wide.csv") -->
<!-- dat$slprad <- pi/180 * dat$slope # convert slope to radians -->
<!-- dat$aspect <- pi/180 * dat$asp # convert aspect to radians -->

<!-- tst <- dat[dat$pplot == 22,] # plot 22 -->
<!-- ``` -->

<!-- ### Lattice Plot of altitudes at the base of trees in plot 22 -->
<!-- ```{r plot22, echo = TRUE, results = "show"} -->
<!-- ## Plot z-values for test plot -->
<!-- plotzvals(tst, slope = "slprad", aspect = "aspect") -->
<!-- ``` -->

