```{r setup, echo = FALSE, results = "hide"}
source("~/work/ecodatascripts/vars/crowns/model/fit-models.R")
specTable <- table(dat$spec)[table(dat$spec) != 0]
elevSpecTable <- table(dat$spec, dat$elevcl)
```

## These scripts predict crown dimensions
Crown depth (distance from lowest to highest point of crown) and crown area (as a horizontal slice through the crown at its widest position) are predicted.  The predictions are constructed using data collected in 1986/87.  Data was available for the following species/elevations:
```{r table, echo = FALSE}
elevSpecTable
```
Due to limited data, models were constructed for the following species/combinations of species: ABBA, PIRU, BECO/BEAL/BEPA (combined into one model), and all hardwoods combined.  Each of the four groups was modeled at three elevations (L/M/H).

## Models
### Crown area
$Crown area = a*BA^b + c*HT$, 
where BA is basal area and HT is height.

### Crown depth
Crown depth is currently just a linear model of tree height:
$Crown depth = a*HT$

## Example predictions
```{r abbas, echo=FALSE}
elev <- c("M")
spp <- "ABBA"
for (ee in elev) {
  dd <- dat[dat$elevcl == ee & dat$spec == spp, ]
  plot(dd$ba, dd$crarea, main = paste("Crown Area Prediction:", spp, "at", ee, "Elevation"), xlab = "Basal Area", ylab = "Crown Area")
  points(dd$ba, predict(crwnAreaMods[[ee]][[tolower(spp)]],
                              newdata = dd), col = "red")
}

## Crown depth
for (ee in elev) {
  dd <- dat[dat$elevcl == ee & dat$spec == spp, ]
  plot(dd$ba, dd$crdepth, main = paste("Crown Depth Prediction:", spp, "at", ee, "Elevation"), xlab = "Basal Area", ylab = "Crown Depth")
  points(dd$ba, predict(crwnDepthMods[[ee]][[tolower(spp)]],
                        newdata = dd), col = "red")
}

```

